AvoidFutRessimpletest

### 2021-12-13 R/AvoidAvRes_withoutcrowns.Rmd
Treefelling work

---
title: 'AvoidAvRes_withcrowns'
author: "Vincyane Badouard"
date: "08/12/2021"
output: html_document
---

@@

# Steps before the treefeling function
```{r}
MainTrail <- sf::st_linestring(matrix(c(286400, 582945,
                                        286400, 583250,
                                        286700, 583250,
                                        286700, 582945,
                                        286400, 582945) # the return
                                      ,ncol=2, byrow=TRUE))

@@

dat <- inventory[2,] %>% # just 1 row (1 tree)
  # force the orientation success for the exemple
  tibble::add_column(TreeFellingOrientationSuccess = "1")
```

@@

# Preliminary steps
```{r}
# Function
Trail <- st_union(MainTrail, ScndTrail) # Our trail will be MainTrail or ScndTrail

@@

# Compute the angle between the tree default position and the shortest way from the foot to the trail
## Right-hand trail
if(TrailPt[1] >= Foot[1]){ # x trail > x foot

  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
                                    c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))

  theta <- 360 - numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
                                       c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
}

@@

# Create future/reserve points
## Loop version
```{r}
# ## To direct to !avoid damage to future and reserve trees!, and foot directed to the trail
# # if (directionalfelling == "1"&& (fuel !="1" || fuel !="2")) {
# 
# # Fut/Res crowns/circumference as points
# FutResAllPoints <- list()
# for (FR in 1:nrow(FutureReserveCrowns)) {
#   ## if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
#   if(FutureReserveCrowns$TreeHeight[FR] <= dat$TreeHeight){
#     
#     FutResAllPoints[[FR]] <- st_cast(st_sfc(FutureReserveCrowns$Crowns[FR]), "POINT", group_or_split = TRUE) # crowns edge in points form
#     
#     ## if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
#   }else if(FutureReserveCrowns$TreeHeight[FR] > dat$TreeHeight){
#     
#     # PROBLEMES de list 
#     FutResAllPoints[[FR]] <- st_point(c(FutureReserveCrowns$Xutm[FR], FutureReserveCrowns$Yutm[FR])) %>%  # the fut/res tree foot point
#       st_buffer(dist = FutureReserveCrowns$DBH[FR]/2) %>%  # create a buffer of DBH diameter
#       st_cast("MULTIPOINT") %>%  # polygon to multipoint
#       st_sfc() %>% 
#       st_cast("POINT", group_or_split = TRUE)
#   }
# }
# # Get all these points back
# do.call(st_union, FutResAllPoints)

@@

## On the data.frame version
```{r}
# if (directionalfelling != "0")

### Compute points
FutResCrownsPoints <- NULL # to start
FutResDBHPoints <- NULL # to start

# if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
if(any(FutureReserveCrowns$TreeHeight <= dat$TreeHeight)){

  FutResCrownsPoints <- FutureReserveCrowns %>% 
    filter(TreeHeight <= dat$TreeHeight) %>% 
    mutate(Crowns = st_cast(Crowns, "MULTIPOINT")) %>% # polygon to multipoint
    summarise(Points = st_combine(Crowns)) # several multipoints to 1
}

# if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
if(any(FutureReserveCrowns$TreeHeight > dat$TreeHeight)){

  FutResDBHPoints <- FutureReserveCrowns %>% 
    filter(TreeHeight > dat$TreeHeight) %>% 
    rowwise() %>% 
    mutate(Points = st_point(c(Xutm, Yutm)) %>% 
             st_buffer(dist = DBH/2) %>% 
             st_cast("MULTIPOINT") %>% 
             st_sfc()) %>% 
    ungroup() %>% 
    summarise(Points = st_combine(Points)) # several multipoints to 1
}

# Get all these points back
if(!is.null(FutResCrownsPoints) & !is.null(FutResDBHPoints)){ # # if smaller and taller trees
  FutResAllPoints <- bind_rows(FutResCrownsPoints, FutResDBHPoints) %>%
    summarise(Points = st_combine(Points)) # 2 multipoints to 1
}

if(!is.null(FutResCrownsPoints) & is.null(FutResDBHPoints)){ # if smaller trees but no tallers
  FutResAllPoints <- FutResCrownsPoints
}

if(!is.null(FutResDBHPoints) & is.null(FutResCrownsPoints)){ # if taller trees but no smallers
  FutResAllPoints <- FutResDBHPoints
}

# Multipoints to points
FutResAllPoints <- st_cast(st_sfc(FutResAllPoints$Points), "POINT", group_or_split = TRUE)

```
## Test time of each version
```{r}
# fun1 <- function(data, H = 30){
#   FutResAllPoints <- list()
#   for (FR in 1:nrow(data)) {
#     ## if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
#     if(data$TreeHeight[FR] <= H){
#       
#       FutResAllPoints[[FR]] <- st_cast(st_sfc(data$Crowns[FR]), "POINT", group_or_split = TRUE) # crowns edge in points form
#       
#       ## if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
#     }else if(data$TreeHeight[FR] > H){
#       
#       # PROBLEMES de list 
#       FutResAllPoints[[FR]] <- st_point(c(data$Xutm[FR], data$Yutm[FR])) %>%  # the fut/res tree foot point
#         st_buffer(dist = data$DBH[FR]/2) %>%  # create a buffer of DBH diameter
#         st_cast("MULTIPOINT") %>%  # polygon to multipoint
#         st_sfc() %>% 
#         st_cast("POINT", group_or_split = TRUE)
#     }
#   }
#   return(do.call(st_union, FutResAllPoints))
# }
# 
# fun2 <- function(data, H = 30){
#   
#   FutResCrownsPoints <- data %>% 
#     filter(TreeHeight <= H) %>% 
#     summarise(Points = st_combine(Crowns))
#   
#   FutResDBHPoints <- data %>% 
#     filter(TreeHeight > H) %>% 
#     rowwise() %>% 
#     mutate(Points = st_point(c(Xutm, Yutm)) %>% 
#              st_buffer(dist = DBH/2) %>% 
#              st_cast("MULTIPOINT") %>% # 
#              st_sfc()) %>% 
#     ungroup() %>% 
#     summarise(Points = st_combine(Points)) # several multipoints to 1
#   
#   FutResAllPoints <- bind_rows(FutResCrownsPoints, FutResDBHPoints) %>% 
#     summarise(Points = st_combine(Points))
#   
#   return(st_cast(st_sfc(FutResAllPoints$Points), "POINT", group_or_split = TRUE))
# }
# 
# microbenchmark::microbenchmark(fun1(FutureReserveCrowns), fun2(FutureReserveCrowns), times = 10)
```

# Distances and angles
```{r}

# Distances between each of these points and Foot
FutResDists <- rep(NA, length(FutResAllPoints)) # empty list for distances
RotationAngle <- rep(NA, length(FutResDists)) # empty list for rotation angles
OppAngToAvoid <- rep(NA, length(RotationAngle)) # empty list for angles to avoid
TrailAnglesToAvoid <- rep(NA, length(RotationAngle)) # empty list for angles to avoid
AnglesToAvoid <- rep(NA, length(RotationAngle)) # empty list for angles to avoid

for (FRP in 1:length(FutResAllPoints)) { # for each point
  FutResDists[[FRP]] <- st_distance(Foot, FutResAllPoints[[FRP]]) # compute the distance for each point

  # If distances < TreeHeight of the tree to be felled
  if(FutResDists[[FRP]] < dat$TreeHeight){
    # sum(FutResDists < dat$TreeHeight) # check av/res trees close to the tree to be felled

    # Compute the angles to the trail of this points
    ## 1st: the rotation angle (between the default position of the tree to cut down, and the position to avoid)
    ### Right-hand fut/res point
    if(FutResAllPoints[[FRP]][1] >= Foot[1]){ # x FRP > x foot

      RotationAngle[[FRP]] <- as.numeric(matlib::angle(
        c(Foot[1] - Foot[1], dat$TreeHeight), # default position
        c(FutResAllPoints[[FRP]][1] - Foot[1], FutResAllPoints[[FRP]][2] - Foot[2]), # position to avoid
        degree = TRUE))

      ### Left-hand fut/res point
    }else if(FutResAllPoints[[FRP]][1] < Foot[1]){ # x FRP < x foot

      RotationAngle[[FRP]] <- 360 - as.numeric(matlib::angle(
        c(Foot[1] - Foot[1], dat$TreeHeight), # default position
        c(FutResAllPoints[[FRP]][1] - Foot[1], FutResAllPoints[[FRP]][2] - Foot[2]), # position to avoid
        degree = TRUE))
      }

    # sum(!is.na(RotationAngle)) # check for how many av/res trees the angle has been computed

    ## Then the angle to the trail: the angle to avoid
    OppAngToAvoid[[FRP]] <- RotationAngle[[FRP]] - 180 - theta
    TrailAnglesToAvoid[[FRP]] <- 180-(90 + OppAngToAvoid[[FRP]])

    # Record their angles if there are in the fall zone ([1; 179°])
    if(TrailAnglesToAvoid[[FRP]] > 1 & TrailAnglesToAvoid[[FRP]] < 179){
      # any(!is.na(TrailAnglesToAvoid) < 179)

      AnglesToAvoid[[FRP]] <- round(TrailAnglesToAvoid[[FRP]], digits = 0)
      # Plus1 <- AnglesToAvoid + 1
      # Moins1 <- AnglesToAvoid - 1
      # Plus2 <- AnglesToAvoid + 2
      # Moins2 <- AnglesToAvoid - 2 # to add a 2° buffer
      # AnglesToAvoid <- c(AnglesToAvoid, Plus1, Moins1) #, Plus2, Moins2
      # sum(!is.na(Plus1)) to check

    }else{AnglesToAvoid <- NULL} # No angles to avoid

    # sum(!is.na(AnglesToAvoid)) # check for how many av/res trees the angle has been computed
  }else{AnglesToAvoid <- NULL} # No angles to avoid
}

```
# Tree felling
```{r}
# Drop the tree between [1; 179°] avoiding the angles of the futures/reserves
if(dat$TreeFellingOrientationSuccess == "1"){

  TreefallOrientation <- c(1:179) # the a priori fall zone (angles to the trail)
  TreefallOrientation <- TreefallOrientation[!TreefallOrientation %in% unique(AnglesToAvoid)] # Remove angles (the fut/res trees) to avoid

@@

  FallenTree <- st_difference(st_union(
    rotatepolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
    rotatepolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
  ))
}

```{r}
ggplot() +
  geom_sf(data = Foot) +
  geom_sf(data = Trail) +
  geom_sf(data = NearestPoints) +
  geom_sf(data = TrailPt) +
  geom_sf(data = FallenTree) +
  geom_sf(data = FutureReserveCrowns) +
  geom_sf(data = FutResCrownsPoints, col = "green") + # smaller trees
  geom_sf(data = FutResDBHPoints, col = "pink")

# geom_sf(data = FutResAllPoints, col = "green")
```

>>>>

---
title: "AvoidAvRes_withoutcrowns"
author: "Vincyane Badouard"
date: "06/12/2021"
output: html_document
---

@@

```{r}
MainTrail <- sf::st_linestring(matrix(c(286400, 582945,
                                        286400, 583250,
                                        286700, 583250,
                                        286700, 582945,
                                        286400, 582945) # the return
                                      ,ncol=2, byrow=TRUE))

@@

dat <- inventory[1,] %>% # just 1 row (1 tree)
  # force the orientation success for the exemple
  tibble::add_column(TreeFellingOrientationSuccess = "1")
```

```{r}
FutureReserveCrowns$Crowns <- st_cast(FutureReserveCrowns$Crowns, "MULTIPOINT")

ggplot() +
   geom_sf(data = getgeometry(FutureReserveCrowns, Crowns), 
           col = "forestgreen")
plot(FutResCrownsPoints)
```

@@

Preliminary steps
```{r}
# Function
Trail <- st_union(MainTrail, ScndTrail) # Our trail will be MainTrail or ScndTrail

@@

# Compute the angle between the tree default position and the shortest way from the foot to the trail
theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
                                  c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))

@@

New work
```{r}
## To direct to !avoid damage to future and reserve trees!, and foot directed to the trail
# if (directionalfelling == "1"&& (fuel !="1" || fuel !="2")) {

# Find the future/reserve on the fall zone
FutRescoord <-  FutureReserveCrowns %>%
  filter(LoggingStatus == "future"| LoggingStatus == "reserve") %>%
  select(Xutm, Yutm) 
st_geometry(FutRescoord) <- NULL

FutResFoots <- st_multipoint(x = as.matrix(FutRescoord)) # all the future/reserve trees foot
FutResFoots <- st_cast(st_sfc(FutResFoots), "POINT", group_or_split = TRUE) # multiple points

## distance to Foot < TreeHeight
FutResDists <- rep(NA, length(FutResFoots)) # empty list for distances
RotationAngle <- rep(NA, length(FutResDists)) # empty list for rotation angles
OppAngToAvoid <- rep(NA, length(RotationAngle)) # empty list for angles to avoid
TrailAnglesToAvoid <- rep(NA, length(RotationAngle)) # empty list for angles to avoid
AnglesToAvoid <- rep(NA, length(RotationAngle)) # empty list for angles to avoid

for (FRF in 1:length(FutResFoots)) { # for each point
  FutResDists[[FRF]] <- st_distance(Foot, FutResFoots[[FRF]]) # compute the distance for each point

  ## angle to the trail
  if(FutResDists[[FRF]] < dat$TreeHeight){
    # sum(FutResDists < dat$TreeHeight) # check av/res trees close to the tree to be felled

    ### 1st: the rotation angle (between the default position of the tree to cut down, and the position to avoid)
    RotationAngle[[FRF]] <- as.numeric(matlib::angle(
      c(Foot[1] - Foot[1], dat$TreeHeight), # default position
      c(FutResFoots[[FRF]][1] - Foot[1], FutResFoots[[FRF]][2] - Foot[2]), # position to avoid
      degree = TRUE))
    # sum(!is.na(RotationAngle)) # check for how many av/res trees the angle has been computed

    ### Then the angle to the trail: the angle to avoid
    OppAngToAvoid[[FRF]] <- RotationAngle[[FRF]] - 180 - theta
    TrailAnglesToAvoid[[FRF]] <- 180-(90 + OppAngToAvoid[[FRF]])

    ## record their angles if there are in the fall zone ([0.1; 179.9°])
    if(TrailAnglesToAvoid[[FRF]] %in% c(0.1:179.9)){

      AnglesToAvoid[[FRF]] <- TrailAnglesToAvoid[[FRF]]
    }else{AnglesToAvoid <- NULL} # No angles to avoid

  }} # temporaires

@@

```{r}
# Drop the tree between [0.1; 179.9°] avoiding the angles of the futures/reserves
if(dat$TreeFellingOrientationSuccess == "1"){

  TreefallOrientation <- c(1:179) # the a priori fall zone (angles to the trail)
  TreefallOrientation <- TreefallOrientation[!TreefallOrientation %in% AnglesToAvoid] # Remove angles (the fut/res trees) to avoid

@@

  FallenTree <- st_difference(st_union(
    rotatepolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
    rotatepolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
  ))
}
```

### 2021-12-13 R/AvoidFutRessimpletest.Rmd
Treefelling work

---
title: 'AvoidAvRes_withcrowns'
author: "Vincyane Badouard"
date: "08/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(Maria)
library(sf)
library(dplyr)
library(nngeo)
library(ggplot2)
```

@@

# Arguments values
```{r}
advancedloggingparameters = loggingparameters()
directionalfelling = "1"
fuel ="0"

@@

# Create future/reserve points
## Loop version
```{r}
# ## To direct to !avoid damage to future and reserve trees!, and foot directed to the trail
# # if (directionalfelling == "1"&& (fuel !="1" || fuel !="2")) {
# 
# # Fut/Res crowns/circumference as points
# FutResAllPoints <- list()
# for (FR in 1:nrow(FutureReserveCrowns)) {
#   ## if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
#   if(FutureReserveCrowns$TreeHeight[FR] <= dat$TreeHeight){
#     
#     FutResAllPoints[[FR]] <- st_cast(st_sfc(FutureReserveCrowns$Crowns[FR]), "POINT", group_or_split = TRUE) # crowns edge in points form
#     
#     ## if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
#   }else if(FutureReserveCrowns$TreeHeight[FR] > dat$TreeHeight){
#     
#     # PROBLEMES de list 
#     FutResAllPoints[[FR]] <- st_point(c(FutureReserveCrowns$Xutm[FR], FutureReserveCrowns$Yutm[FR])) %>%  # the fut/res tree foot point
#       st_buffer(dist = FutureReserveCrowns$DBH[FR]/2) %>%  # create a buffer of DBH diameter
#       st_cast("MULTIPOINT") %>%  # polygon to multipoint
#       st_sfc() %>% 
#       st_cast("POINT", group_or_split = TRUE)
#   }
# }
# # Get all these points back
# do.call(st_union, FutResAllPoints)

## On the data.frame version
```{r}
# if (directionalfelling != "0")

@@

```
## Test time of each version
```{r}
# fun1 <- function(data, H = 30){
#   FutResAllPoints <- list()
#   for (FR in 1:nrow(data)) {
#     ## if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
#     if(data$TreeHeight[FR] <= H){
#       
#       FutResAllPoints[[FR]] <- st_cast(st_sfc(data$Crowns[FR]), "POINT", group_or_split = TRUE) # crowns edge in points form
#       
#       ## if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
#     }else if(data$TreeHeight[FR] > H){
#       
#       # PROBLEMES de list 
#       FutResAllPoints[[FR]] <- st_point(c(data$Xutm[FR], data$Yutm[FR])) %>%  # the fut/res tree foot point
#         st_buffer(dist = data$DBH[FR]/2) %>%  # create a buffer of DBH diameter
#         st_cast("MULTIPOINT") %>%  # polygon to multipoint
#         st_sfc() %>% 
#         st_cast("POINT", group_or_split = TRUE)
#     }
#   }
#   return(do.call(st_union, FutResAllPoints))
# }
# 
# fun2 <- function(data, H = 30){
#   
#   FutResCrownsPoints <- data %>% 
#     filter(TreeHeight <= H) %>% 
#     summarise(Points = st_combine(Crowns))
#   
#   FutResDBHPoints <- data %>% 
#     filter(TreeHeight > H) %>% 
#     rowwise() %>% 
#     mutate(Points = st_point(c(Xutm, Yutm)) %>% 
#              st_buffer(dist = DBH/2) %>% 
#              st_cast("MULTIPOINT") %>% # 
#              st_sfc()) %>% 
#     ungroup() %>% 
#     summarise(Points = st_combine(Points)) # several multipoints to 1
#   
#   FutResAllPoints <- bind_rows(FutResCrownsPoints, FutResDBHPoints) %>% 
#     summarise(Points = st_combine(Points))
#   
#   return(st_cast(st_sfc(FutResAllPoints$Points), "POINT", group_or_split = TRUE))
# }
# 
# microbenchmark::microbenchmark(fun1(FutureReserveCrowns), fun2(FutureReserveCrowns), times = 10)
```

@@

@@

    # Compute the angles to the trail of this points
    ## 1st: the rotation angle (between the default position of the tree to cut down, and the position to avoid)
    ### Right-hand fut/res point
    if(FutResAllPoints[[FRP]][1] >= Foot[1]){ # x FRP > x foot

      RotationAngle[[FRP]] <- as.numeric(matlib::angle(
        c(Foot[1] - Foot[1], dat$TreeHeight), # default position
        c(FutResAllPoints[[FRP]][1] - Foot[1], FutResAllPoints[[FRP]][2] - Foot[2]), # position to avoid
        degree = TRUE))

      ### Left-hand fut/res point
    }else if(FutResAllPoints[[FRP]][1] < Foot[1]){ # x FRP < x foot

      RotationAngle[[FRP]] <- 360 - as.numeric(matlib::angle(
        c(Foot[1] - Foot[1], dat$TreeHeight), # default position
        c(FutResAllPoints[[FRP]][1] - Foot[1], FutResAllPoints[[FRP]][2] - Foot[2]), # position to avoid
        degree = TRUE))
      }

@@

    ## Then the angle to the trail: the angle to avoid
    OppAngToAvoid[[FRP]] <- RotationAngle[[FRP]] - 180 - theta
    TrailAnglesToAvoid[[FRP]] <- 180-(90 + OppAngToAvoid[[FRP]])

@@

      AnglesToAvoid[[FRP]] <- round(TrailAnglesToAvoid[[FRP]], digits = 0)
      # Plus1 <- AnglesToAvoid + 1
      # Moins1 <- AnglesToAvoid - 1
      # Plus2 <- AnglesToAvoid + 2
      # Moins2 <- AnglesToAvoid - 2 # to add a 2° buffer
      # AnglesToAvoid <- c(AnglesToAvoid, Plus1, Moins1) #, Plus2, Moins2
      # sum(!is.na(Plus1)) to check

@@

```
# Tree felling
```{r}
# Drop the tree between [1; 179°] avoiding the angles of the futures/reserves
if(dat$TreeFellingOrientationSuccess == "1"){

@@

  FallenTree <- st_difference(st_union(
    rotatepolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
    rotatepolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
  ))
}

```{r}
ggplot() +
  geom_sf(data = Foot) +
  geom_sf(data = Trail) +
  geom_sf(data = NearestPoints) +
  geom_sf(data = TrailPt) +
  geom_sf(data = FallenTree) +
  geom_sf(data = FutureReserveCrowns) +
  geom_sf(data = FutResCrownsPoints, col = "green") + # smaller trees
  geom_sf(data = FutResDBHPoints, col = "pink")

>>>>

---
title: "AvoidFutRessimpletest"
author: "Vincyane Badouard"
date: "10/12/2021"
output: html_document
---
```{r}
library(Maria)
library(sf)
library(dplyr)
library(nngeo)
library(ggplot2)
```

@@

Our tree to be felled
```{r}
dat$Xutm <- 286546.1
dat$Yutm <- 583029.1
```
# A buffer around the Foot
```{r}
FootBuffer <- dat %>% 
  mutate(Points = st_point(c(Xutm, Yutm)) %>% 
           st_buffer(dist = CrownDiameter/2) %>% 
           st_cast("MULTIPOINT") %>% 
           st_sfc())

# Multipoints to points
FootBuffer <- st_cast(st_sfc(FootBuffer$Points), "POINT", group_or_split = TRUE)

2 av/res trees
```{r}
FutureReserveCrowns <- FutureReserveCrowns[1:2,]

# at the same y than the tree to be felled
# 1 on the right side
FutureReserveCrowns[1,]$Xutm <- dat$Xutm + 30
FutureReserveCrowns[1,]$Yutm <- dat$Yutm + 10

# 1 on the left side
FutureReserveCrowns[2,]$Xutm <- dat$Xutm - 30 
FutureReserveCrowns[2,]$Yutm <- dat$Yutm + 10

# # Re-compute the crown
st_geometry(FutureReserveCrowns) <- NULL

FutureReserveCrowns <- FutureReserveCrowns %>%
  createcanopy() %>% # create all inventory crowns in the 'Crowns' column
  getgeometry(Crowns)

@@

# Compute points
```{r}
# if (directionalfelling != "0")

@@

@@

# Only Foots 
# FutResAllPoints <- FutureReserveCrowns %>% 
#    select(Xutm, Yutm)
# 
# FutResFoots <- st_multipoint(x = as.matrix(FutResAllPoints)) # all the future/reserve trees foot
# FutResAllPoints <- st_cast(st_sfc(FutResFoots), "POINT", group_or_split = TRUE) # multiple points

@@

    # Compute the angles to the trail of this points
    ## 1st: the rotation angle (between the default position of the tree to cut down, and the position to avoid)
    for (P in 1:length(FootBuffer)) { # for each point of the Foot buffer

      ### Right-hand fut/res point
      if(FutResAllPoints[[FRP]][1] >= FootBuffer[[P]][1]){ # x FRP > x foot

        RotationAngle[[FRP]] <- as.numeric(matlib::angle(
          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], dat$TreeHeight), # default position
          c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - FootBuffer[[P]][2]), # position to avoid
          degree = TRUE))

        ### Left-hand fut/res point
      }else if(FutResAllPoints[[FRP]][1] < FootBuffer[[P]][1]){ # x FRP < x foot

        RotationAngle[[FRP]] <- 360 - as.numeric(matlib::angle(
          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], dat$TreeHeight), # default position
          c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - FootBuffer[[P]][2]), # position to avoid
          degree = TRUE))
      }
    }

@@

    ## Then the angle to the trail: the angle to avoid
    OppAngToAvoid[[FRP]] <- RotationAngle[[FRP]] - 180 - theta # valeurs négatives c'est là le prblm
    TrailAnglesToAvoid[[FRP]] <- 180-(90 + OppAngToAvoid[[FRP]])

    TrailAnglesToAvoid[[FRP]] <- round(TrailAnglesToAvoid[[FRP]], digits = 0)

    if(TrailAnglesToAvoid[[FRP]] >= 360) TrailAnglesToAvoid[[FRP]] <- TrailAnglesToAvoid[[FRP]] - 360

@@

      AnglesToAvoid[[FRP]] <- TrailAnglesToAvoid[[FRP]]
      # Plus1 <- AnglesToAvoid + 1
      # Moins1 <- AnglesToAvoid - 1
      # Plus2 <- AnglesToAvoid + 2
      # Moins2 <- AnglesToAvoid - 2 # to add a 2° buffer
      # AnglesToAvoid <- c(AnglesToAvoid, Plus1, Moins1) #, Plus2, Moins2
      # sum(!is.na(Plus1)) to check

@@

# Tree felling
```{r}
# Drop the tree between [1; 179°] avoiding the angles of the futures/reserves
if(dat$TreeFellingOrientationSuccess == "1"){

@@

  FallenTree <- st_difference(st_union(
    rotatepolygon(Trunk, angle = RandomAngle, fixed = Foot), # turned trunk
    rotatepolygon(Crown, angle = RandomAngle, fixed = Foot) # turned crown
    ))
}
```

# Plot
```{r}
ggplot() +
  geom_sf(data = Foot) +
  geom_sf(data = Trail) +
  geom_sf(data = NearestPoints) +
  geom_sf(data = TrailPt) +
  geom_sf(data = FallenTree) +
  geom_sf(data = FutResAllPoints) + # FutureReserveCrowns
  geom_sf(data = FutResCrownsPoints, col = "green") + # smaller trees
  geom_sf(data = FutResDBHPoints, col = "pink") +
  geom_sf(data = FootBuffer)
